TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-06-10 paper/draft.tex
little tweaks

Additionally, the low masses of M dwarfs make for easier detection of planets by radial velocity offset detections \citep{Trifonov:2018}, high planet-to-star radii ratios make for easier detection of exoplanet transits in light curve observations \citep{Nutzman:2008}, and shorter orbital periods (for a fixed stellar insulation flux) allow for new planet discovery in less observation time than their higher mass counterparts. For these reasons, M dwarfs are primary candidates for exoplanet searches, including by the NASA \kepler\ \citep[e.g.,][]{Dressing2015} and Transiting Exoplanet Survey Satellite (\tess) \citep[e.g.,][]{Muirhead:2018} missions. As a result, detailed and precise knowledge of M dwarf chemical compositions has become key to constraining the the properties, formation scenarios, and atmospheric conditions of potentially habitable exoplanets observable with {\it JWST}.

Advances in instrumentation with the launch of several spectroscopic surveys in the past decade, such as the Sloan Digital Sky Survey (SDSS), and the Large Sky Area Multi-Object Fiber Spectroscopic Telescope (LAMOST) have dramatically increased the sample of known M dwarfs (\citealt{West:2011}, \citealt{Guo:2015} with catalogs of over 70,000 sources), enabling studies of M dwarf abundances on both exoplanet and Galactic scales.
The launch of the Apache Point Observatory Galactic Evolution Experiment (\apogee; \citealt{Majewski:2015}) survey as part of the Sloan Digital Sky Survey III mission \citep{Eisenstein:2011} has introduced the largest sample of M dwarfs observed with high resolution spectroscopy \citep{Desphande:2013}. \apogee\ pipeline measurements of $\teff$ and $\feh$ \citep{Perez:2016} for M dwarfs have only been determined to 100\,K and 0.18\,dex down to $T_{\rm eff}\sim3550\,$K using atmospheric models \citep{Schmidt:2016}.

>>>>

Additionally, the low masses of M dwarfs make for easier detection of planets by radial velocity offset detections \citep{Trifonov:2018}, high planet-to-star radii ratios make for easier detection of exoplanet transits in light curve observations \citep{Nutzman:2008}, and shorter orbital periods (for a fixed stellar insulation flux) allow for new planet discovery in less observation time than their higher mass counterparts. For these reasons, M dwarfs are primary candidates for exoplanet searches, including by the NASA \kepler\ \citep[e.g.,][]{Dressing2015} and Transiting Exoplanet Survey Satellite (\tess) \citep[e.g.,][]{Muirhead:2018} missions. As a result, detailed and precise knowledge of M dwarf chemical compositions has become key to constraining the the properties, formation scenarios, and atmospheric conditions of potentially habitable exoplanets observable with {\sl JWST}.

Advances in instrumentation with the launch of several spectroscopic surveys in the past decade, such as the Sloan Digital Sky Survey (SDSS), and the Large Sky Area Multi-Object Fiber Spectroscopic Telescope (LAMOST) have dramatically increased the sample of known M dwarfs (\citealt{West:2011}, \citealt{Guo:2015} with catalogs of over 70,000 sources), enabling studies of M dwarf abundances on both exoplanet and Galactic scales.
The launch of the Apache Point Observatory Galactic Evolution Experiment (\apogee; \citealt{Majewski:2015}) survey as part of the Sloan Digital Sky Survey III/IV mission \citep{Eisenstein:2011,Blanton:2017} has introduced the largest sample of M dwarfs observed with high resolution spectroscopy \citep{Desphande:2013}. \apogee\ pipeline measurements of $\teff$ and $\feh$ \citep{Perez:2016} for M dwarfs have only been determined to 100\,K and 0.18\,dex down to $T_{\rm eff}\sim3550\,$K using atmospheric models \citep{Schmidt:2016}.
